Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2017-03-08 manuscript/supplemental_material.Rnw
fix placenta typo in supp table label

<<tissue_specificity_index_of_placenta_core_genes,echo=FALSE,results="asis">>=
print(xtable(core.placenta.genes.tsi[order(-`Median FPKM`),
                                     list(`Gene name`,
                                          `Tissue Specificity Index`,
                                          `Median FPKM`,
                                          `Gene Type`
                                          )],
             digits=2,
             display=c("s","s","f","f","s"),
             caption=c("Tissue specificity index~\\cite{Yanai.ea2005:Genome-widemidrangetranscriptionprofiles} (calculated based on the Human Protein Atlas version 16.1 RNA-seq data \\cite{Uhlén.ea2015:ProteomicsTissue-basedmapof}) of Placenta Core Genes ordered by median expression with housekeeping status~\\cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited} indicated.",
                       "Tissue specificity of Placenta Core Genes"
                       ),
             label="tab:tissue_specificity_index_of_plaenta_core_genes"
             ),
      include.rownames=FALSE,
      booktabs=TRUE,
      math.style.exponents=TRUE,
      size="\\footnotesize",
      caption.placement="top",
      tabular.environment="longtable",
      floating=FALSE
      )
@

>>>>

<<tissue_specificity_index_of_placenta_core_genes,echo=FALSE,results="asis">>=
print(xtable(core.placenta.genes.tsi[order(-`Median FPKM`),
                                     list(`Gene name`,
                                          `Tissue Specificity Index`,
                                          `Median FPKM`,
                                          `Gene Type`
                                          )],
             digits=2,
             display=c("s","s","f","f","s"),
             caption=c("Tissue specificity index~\\cite{Yanai.ea2005:Genome-widemidrangetranscriptionprofiles} (calculated based on the Human Protein Atlas version 16.1 RNA-seq data \\cite{Uhlén.ea2015:ProteomicsTissue-basedmapof}) of Placenta Core Genes ordered by median expression with housekeeping status~\\cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited} indicated.",
                       "Tissue specificity of Placenta Core Genes"
                       ),
             label="tab:tissue_specificity_index_of_placenta_core_genes"
             ),
      include.rownames=FALSE,
      booktabs=TRUE,
      math.style.exponents=TRUE,
      size="\\footnotesize",
      caption.placement="top",
      tabular.environment="longtable",
      floating=FALSE
      )
@
